\documentclass[]{article}

\title{Lololo}
\author{Lalala}
\date{06-07-08}
\begin{document}
	\maketitle
	\subsection*{title}
	Subsection not numbered
	\subsection{title}
	Subsection numbered
	\subsubsection[short title]{title}
	Subsubsection numbered.
	There are no subsubsubsections.... I think you don't need that many. Also you don't need a section to have a subsection (Not required, not very nice!)
	Please note how all the sections and subsections get numbered and get a nice format (boldface and bigger size).
	%\subsubsubsection there is no subsubsubsection
	\section{Font format} 
	This will produce \textit{italicized}.
	This will produce \textbf{bold}.
	This will produce \textsc{small caps}.
	This will produce \texttt{typewriter}.
	\section{Font size}
	Please excuse my dear aunt \begin{Huge}Sally\end{Huge}.
	Please excuse my dear aunt \begin{huge}Sally\end{huge}.
	Please excuse my dear aunt \begin{LARGE}Sally\end{LARGE}.
	Please excuse my dear aunt \begin{Large}Sally\end{Large}.
	Please excuse my dear aunt \begin{large}Sally\end{large}
	Please excuse my dear aunt \begin{normalsize}Sally\end{normalsize}.
	Please excuse my dear aunt \begin{small}Sally\end{small}.
	Please excuse my dear aunt \begin{footnotesize}Sally\end{footnotesize}.
	Please excuse my dear aunt \begin{scriptsize}Sally\end{scriptsize}.
	Please excuse my dear aunt \begin{tiny}Sally\end{tiny}.
	\section{Alignment}
	\begin{center}
		Please excuse my dear aunt Sally.
	\end{center}
	\begin{flushleft}
		Please excuse my dear aunt Sally.
	\end{flushleft}
	\begin{flushright}
		Please excuse my dear aunt Sally.
	\end{flushright}
\centering % everything that comes after this is going to be centered
\Large
Apples, oranges, bananas. \normalsize Normal size again!
\end{document}

